### 2024-04-22 scripts/02-data_cleaning.qmd
update

```{r}
#### Workspace setup ####
library(tidyverse)
library(jsonlite)
library(readr)
library(janitor)
library(dplyr)

```

@@

# Write the cleaned data frame to a CSV file
write_csv(cleaned_pocket_area_data, csv_file)

```

>>>>

```{r}
#### Workspace setup ####
library(tidyverse)
library(jsonlite)
library(readr)
library(janitor)
library(dplyr)
```

@@

# Write the cleaned data frame to a CSV file
write_csv(cleaned_pocket_area_data, csv_file)
```
